Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-02-18 draft.tex
changes to related work

@@

	approach using perceptible features for classification in their works. They trained and tested
	using the dataset of the ADD2022 Challenge \cite{yi_add_2024} and a simple model with a single
	hidden layer, resulting in lackluster performance in 2022, with better results using an
	expanded and improved feature set in 2023.

@@

	various neural networks in their experiments. Overall, the combination of perceptible and
	imperceptible features was able to produce the best performance results of the experiments,
	which were performed as well on the dataset of the ASV2022 Challenge \cite{yi_add_2024}.

@@

>>>>

	Yang et al. \cite{yang_robust_2024} demonstrate a multi-feature comparison, as well as a
	feature selection method, with the goal of maximizing model efficiency. They run experiments
	with several hand-crafted features as well as learned features. They train and test using
	three datasets, ASVSpoof2019 \cite{wang_asvspoof_2020}, ASV2021 \cite{liu_asvspoof_2023} and
	In-the-Wild \cite{muller_does_2022}, presenting their results for each features, as well as
	the results of their selection and classification fusion methods.

@@

	approach using perceptible features for classification in their works. They developed a
	perceptron-architecture with a single hidden layer, and trained and tested using the dataset
	of the ADD2022 Challenge \cite{yi_add_2024}, resulting in lackluster performance in 2022, with
	better results using an expanded and improved feature set in 2023.

@@

	various neural networks in their experiments. With their combination of perceptible and
	imperceptible features, they were able to produce the best performance results of their
	experiments, which were performed as well on the dataset of the ASV2022 Challenge
	\cite{yi_add_2024}.

@@

	There have also been some efforts in the previous research to pair synthetic voice detection
	models with explainable methods.
